### 2023-09-26 main.tex
fixed

for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$.

@@

 We first define the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$. Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.

@@

We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at left of site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at right of site $L$. The generator reads

@@

with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$

@@

The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s. \\ \\

@@

\paragraph{Action on the occupation variable of $\mathcal{L}_{x,+1}^{rd}$}

@@

\paragraph{Action on the occupation variable of $\mathcal{L}_{left}^{rd}$}

@@

Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation where the discrete Laplacians of all species are coupled and linear reaction terms are present. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question we addressed to in the beginning of this section.

@@

The dual  process $(\bm{\xi}(t))_{t\geq 0}$ takes values in the enlarged state space
	\widetilde{\Omega}=\mathbb{N}_{0}^{N-1}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N-1}
We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
where dual particles will accumulate in the course of time. 
We denote the configurations $\bm{\xi} \in \widetilde\Omega$  as
	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
The duality function is given by

@@

The dual process is defined by its generator, which reads

@@

\subsubsection{Proof of duality}

@@

Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry.

\paragraph{Duality for $H_{x,x+1}^{c}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

\paragraph{Duality for $H_{x,x+1}^{m}$} We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives

>>>>

for $ x\in\{1,\ldots,L\}\quad a\in\{1,2\}$  and where $\overline{a}=1$ if $a=2$ and $\overline{a}=1$ if $a=2$. Here $\Delta_{L}\rho(x,t)=\rho_{a}(x+1,t)+\rho_{a}(x-1,t)-2\rho_{a}(x,t)$.

@@

 We construct the process on a chain in order to obtain \eqref{NSpeciesRD} for the evolution of the average occupation variable of type $a$. Once we have found such a process, we construct the Lie algebraic description and we use it to prove absorbing duality.

@@

We consider the geometry of a chain of length $L$, where we assume that a reservoir with parameters $(\alpha_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $1$ and a reservoir with parameters $(\beta_{a})_{a\in\{1,\ldots,N\}}$ is attached at site $L$. The state space is $\Omega$ given in \eqref{stateSpace-Chain} and the generator reads

@@

with $\mathcal{L}_{x,x+1}$ is the edge \eqref{edgeGenerator} of the multi-species stirring process and, for any function $f:\Omega\to \mathbb{R}$ and for any $c\in \{1,\ldots,N-2\}$ we introduce

@@

The boundary generator $\mathcal{L}_{right}^{rd}$ is defined analugosly, but the $\alpha$'s are replaced by $\beta$'s and the boundary densities are considered at site $L+1$. \\ \\

@@

\paragraph{Action of $\mathcal{L}_{x,+1}^{rd}$ on the occupation variable}

@@

\paragraph{Action of $\mathcal{L}_{left}^{rd}$ on the occupation variable}

@@

Therefore, using the action of $\mathcal{L}^{rd}$ expressed by \eqref{DifferenceEquation} and \eqref{actionBDLine} we obtain a system of $N-1$ difference-differential equation\eqref{NSpeciesRD} where the discrete Laplacians of all species are coupled and linear reaction terms are present that we aimed for. For these reasons, this model is a generalization to $N$ species and to maximal occupation $\nu$ of the one studied in \cite{casini2022uphill}. This answers the first question we addressed to in the beginning of this subsection.

@@

The dual  process $(\bm{\xi}(t))_{t\geq 0}$ still takes values in the enlarged state space \eqref{stateSpaceDUAL-Chain}
%	\widetilde{\Omega}=\mathbb{N}_{0}^{N}\times  \bigtimes_{x\in V} \Omega_{x}\times \mathbb{N}_{0}^{N}
%We associate an ``extra site'', denoted by $0$ and $L+1$ attached to $1$ and $L$ respectively,
%where dual particles will accumulate in the course of time. 
We denote the configurations $\bm{\xi} \in \widetilde\Omega$ 
%	\bm{\xi}=\left(\xi_{1}^{0},\ldots,\xi_{N}^{0}\right)\otimes\left(\xi_{1}^{x},\ldots,\xi_{N}^{x}\right)^{\otimes L}\otimes \left(\xi_{1}^{L+1},\ldots,\xi_{N}^{L+1}\right)
%where the component $\xi_{a}^{x}$ is interpreted as the number of dual particles of type $a\in \{1,\ldots,N\}$ at site $x$, 
%and the component $\xi_{a}^{0},\xi_{a}^{L+1}$  give the number at the extra sites. \\
The duality function is still given by

@@

The dual process is defined by the dual generator

@@

\paragraph{Proof of duality}

@@

Since the matrix $R_{x}$ is the same as in Section \ref{sectionDuality}, we shall show that $\mathcal{H}_{x,x+1}^{c}$ and $\mathcal{H}_{x,x+1}^{m}$ have $\exp{(E^{x})}\exp{(E^{x+1})}$ as a symmetry. \\
%\paragraph{Duality for $H_{x,x+1}^{c}$}
 We compute the commutator between $\mathcal{H}_{x,x+1}^{c}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}(E_{bN}^{x})$. Using \eqref{eq:comgl}, the bilinearity and associativity of the Kronecker product and the bilinearity of the brackets we obtain 

@@

%\paragraph{Duality for $H_{x,x+1}^{m}$} 
We compute the commutator between $\mathcal{H}_{x,x+1}^{m}$ and $\sum_{d=1}^{N-1}(E_{dN}^{x})\otimes \sum_{k=1}^{N-1}E_{bN}^{x}$. The prof is similar and gives
